Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
something about the acceleration

We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, is 
based on~\cite{Monteiro16}, but 
enhanced to include evaluation of quantization effects and safety properties
over the state space. In the second approach, we use a verification engine
based on XXXXXXX
\todo{something about the acceleration verification engine}

>>>>

We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but 
enhanced to include evaluation of quantization effects and safety properties
over the state space. In the second approach, we use a verification engine
based on abstract acceleration~\cite{cattaruzza2015unbounded} than avoids the explicit 
unwinding the transition system necessarily for the first approach.
